Application of a Discontinuous Petrov-Galerkin method to problems in compressible flow

### 2012-09-18 docs/Jesse/Vienna/pres.tex

\title[A DPG method for Compressible Flow]{Application of a Discontinuous Petrov-Galerkin method to compressible flow problems}
\date{Sept 12, 2012}
\author[J. Chan, L. Demkowicz, R. Moser]{Jesse Chan\\ Supervisors: Leszek Demkowicz, Robert Moser}

@@

\frame{
\frametitle{Compressible Navier-Stokes equations}
\begin{columns}[c]
\begin{column}{.55\textwidth}
Numerical difficulties:
\begin{itemize}
\item{} Resolving solution features (sharp, localized viscous-scale phenomena)
\begin{itemize}
\item{} Shocks
\item{} Boundary layers - resolution needed for drag/load
\end{itemize}
\item{} Stability of numerical schemes
\begin{itemize}
\item{} Coarse/adaptive grids
\item{} Higher order
\end{itemize}
\item{} Stabilized methods
\begin{itemize}
\item{} Stabilization parameters
\item{} Higher-order
\end{itemize}
\end{itemize}
\end{column}
\begin{column}{.4\textwidth}
\begin{figure}
\centering
\subfigure{\includegraphics[scale = .6]{figs/compFlowPics/airfoil_mesh.png}}
\subfigure{\includegraphics[scale=.3]{figs/SUPG.png}}
\end{figure}
\end{column}
\end{columns}
}

\section{The DPG Method}
\frame{
\frametitle{DPG: a minimum residual method via optimal testing}
Given a trial space $U$ and Hilbert test space $V$,
\[
b(u,v) = \ell(v) \Longleftrightarrow Bu = \ell, \quad 
\left.\begin{array}{cl}
\langle Bu,v\rangle_V &\coloneqq b(u,v)\\
\langle \ell,v\rangle_V &\coloneqq \ell(v).
\end{array}\right\}
\]
We seek to minimize the \textcolor{red}{dual residual} over $U_h \subset U$
\[
J(u_h) = \frac{1}{2}\|Bu_h-\ell\|_{V'}^2 = \frac{1}{2}\left\|R_V^{-1}(Bu_h-\ell)\right\|_V^2.
\]
where $R_V: V \to V'$ is the isometric Riesz map
\[
\langle R_V v,\delta v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
\]
Conditions for minimization of the convex functional give
\[
b(u_h,v_{\delta u}) = \ell(v_{\delta u}), \quad \forall \delta u \in U_h, \quad v_{\delta u} \coloneqq R_V^{-1}B\delta u.
\]
}

@@

@@

\frame{
\frametitle{Graph norm under convection-diffusion}
The graph norm\footnote{\bibentry{Bui-ThanhDemkowiczGhattas11b}} for convection-diffusion gives exceptional stability.  %, this norm is defined elementwise
\begin{align*}
\|\left(v,\tau\right)\|_{V(K)}^2 =& \| \div \tau - \beta \cdot \grad v\|_{L^2(K)}^2 + 
\| \epsilon^{-1} \tau + \grad v \|_{L^2(K)}^2 +
\|v\|_{L^2(K)}^2.
\end{align*}
Problem with this test norm: approximability of test functions.
\begin{figure}[!h]
\centering
\includegraphics[scale=.16]{figs/opt.png}
\caption{Components of optimal test functions for flux $\widehat{f}_n$ on the \emph{right-hand} side of a unit element for $\epsilon = 0.01$. }
\label{fig:optTestBoundary}
\end{figure}
}

\frame{
\frametitle{Determining an alternative test norm}
%Recall the convection-diffusion bilinear form.  %Let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$. 
\vspace{-.85cm}
\begin{align*}%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),\left( v, \tau \right)\right) 
b(\boldsymbol U,\boldsymbol V) = \left(u,\div \tau - \beta \cdot \grad
v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} + \text{boundary terms}
% - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}
\end{align*}
Recover $\nor{u}^2_{L^2(\Omega)}$ with conforming $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
\begin{align*}
\left.
\begin{array}{cl}
\div\tau - \beta \cdot \grad v   &= u\\
\frac{1}{\epsilon}\tau + \grad v &= 0
\end{array}
\right. ,
\quad
\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gamma}, \LRa{ \widehat{f}_n,\jump{v} }_{\Gamma} = 0
\end{align*}
``Necessary'' conditions for robustness --- 
\[
\nor{u}^2_{L^2(\Omega)} = b\LRp{{\boldsymbol U},\LRp{v,\tau}} = \frac{b\LRp{{\boldsymbol U},\LRp{v,\tau}}}{\nor{\LRp{v,\tau}}_V} \nor{\LRp{v,\tau}}_V \leq \nor{\boldsymbol U}_E \nor{\LRp{v,\tau}}_V
\]
Let $\lesssim$ denote a robust bound - \textcolor{red}{if $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$}, then we have that
\[
\nor{u}_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
\]
\textbf{Main idea: the \textcolor{red}{test norm} should measure \textcolor{red}{adjoint solutions} robustly.}
}

@@

\begin{figure}[!h]
\centering
\subfigure[Dirichlet inflow]{\includegraphics[scale=.35]{figs/dirichletBC.png}}
\subfigure[``Convection'' inflow]{\includegraphics[scale=.35]{figs/newBC.png}}
\caption{DPG solutions to convection-diffusion for both inflow conditions using an $H^1$ test norm.}
\end{figure}
}

@@

%On domain $\Omega = [0,1]^2$, with $\beta = (1,0)^T$, $ f = 0$ and boundary conditions
%\begin{align*}
%\widehat{\beta_nu - \sigma_n} &= \widehat{f}_n = u_0, \quad \beta_n \leq 0\\
%\widehat{u} &= 0, \quad \beta_n > 0
%\end{align*}
Experiments done using Camellia\footnote{\bibentry{Camellia}} and a boundary layer solution.
%\begin{figure}
%\centering
%\subfigure{
%\includegraphics[scale=.23]{figs/wallBC_exact_u.png}
%}
%\subfigure{
%\includegraphics[scale=.23]{figs/wallBC_exact_sigx.png}
%}
%\subfigure{
%\includegraphics[scale=.23]{figs/wallBC_exact_sigy.png}
%}
%\caption{Exact solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
%\end{figure}
\begin{figure}
\centering
\subfigure{
\includegraphics[scale=.33]{figs/errorrates_wallBC.png}
}
\subfigure{
\includegraphics[scale=.33]{figs/L2energyratio_wallBC.png}
}
%\subfigure{
%\includegraphics[scale=.22]{figs/u_pointdiff_wallBC.png}
%}
\caption{$L^2$/energy errors and their ratio for $\epsilon = .01, .001, .0001$.}
\end{figure}
}

@@

\frame{
\frametitle{Extrapolation of test norms}
%\begin{columns}
%\begin{column}{.48\textwidth}
Convection-diffusion:
\begin{align*}
\div \left(\textcolor{red}{\beta u} - \textcolor{blue}{\sigma}\right) &= f\\
\frac{1}{\epsilon}\sigma - {\grad u} &= 0.
\end{align*}
Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},w\}$,
\begin{align*}
\div \left(\textcolor{red}{A_{\rm invisc}U} - \textcolor{blue}{A_{\rm visc}\Sigma}\right) &= R_{\rm conserv}(U,\Sigma)\\
E_{\rm visc} \Sigma - \grad U &= R_{\rm constit}(U,\Sigma)
\end{align*}
where $R_{\rm conserv}(U,\Sigma)$ and $R_{\rm constit}(U,\Sigma)$ are the conservation/constitutive residuals.
}
%\addtocounter{framenumber}{-1}
\frame{
\frametitle{Extrapolation of test norms}
%\begin{columns}
%\begin{column}{.48\textwidth}
Convection-diffusion:
\begin{align*}
\div \left(\beta u - \sigma\right) &= f\\
\textcolor{red}{\frac{1}{\epsilon}\sigma} - \textcolor{blue}{\grad u} &= 0.
\end{align*}
Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},w\}$,
\begin{align*}
\div \left({A_{\rm invisc}U} - {A_{\rm visc}\Sigma}\right) &= R_{\rm conserv}(U,\Sigma)\\
\textcolor{red}{E_{\rm visc} \Sigma} - \textcolor{blue}{\grad U} &= R_{\rm constit}(U,\Sigma)
\end{align*}
where $R_{\rm conserv}(U,\Sigma)$ and $R_{\rm constit}(U,\Sigma)$ are the conservation/constitutive residuals.
}

@@

\frame{
\frametitle{Refinement level 0}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u0.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T0.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh0.png}}
\end{figure}
}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 1}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u1.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T1.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh1.png}}
\end{figure}
}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 2}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u2.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T2.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh2.png}}
\end{figure}
}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 3}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u3.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T3.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh3.png}}
\end{figure}
}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 4}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u4.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T4.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh4.png}}
\end{figure}
}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 5}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u5.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T5.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh5.png}}
\end{figure}
}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 6}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u6.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T6.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh6.png}}
\end{figure}
}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 7}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u7.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T7.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh7.png}}
\end{figure}
}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 8}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u8.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T8.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh8.png}}
\end{figure}
}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 9}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u9.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T9.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh9.png}}
\end{figure}
}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 10}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u10.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T10.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh10.png}}
\end{figure}
}
\setcounter{subfigure}{0}

@@

%\input{futureWork}
%\input{extendedSlides}

>>>>

\title[A DPG method for Compressible Flow]{Application of a Discontinuous Petrov-Galerkin method to problems in compressible flow}
\date{ECCOMAS: Sept 12, 2012}
\author[J. Chan, N. Roberts, L. Demkowicz, R. Moser]{Jesse Chan, Nathan Roberts\\ Supervisors: Leszek Demkowicz, Robert Moser}

@@

\frame{
\frametitle{Compressible Navier-Stokes equations}
\begin{columns}[c]
\begin{column}{.55\textwidth}
Numerical difficulties:
\begin{itemize}
\item{} Resolving solution features (sharp, localized viscous-scale phenomena)
\begin{itemize}
\item{} Shocks
\item{} Boundary layers - resolution needed for drag/load
\end{itemize}
%\item{} Stability of numerical schemes 
%\begin{itemize}
%\item{} Coarse grids
%\item{} Higher order
%\end{itemize}
\item{} Problems of \emph{discrete coercivity} and \emph{robustness}: 
\begin{align*}
b(v,v) &\geq \epsilon\nor{v}_{H^1_0}^2, \quad (\text{if at all}),\\
\nor{u-u_h} &\leq C_\epsilon \inf_{w_h} \nor{u-w_h}.
\end{align*}
\item{} Current fix: stabilization%SUPG aims to solve both simultaneously.
\end{itemize}
\end{column}
\begin{column}{.4\textwidth}
\begin{figure}
\centering
\subfigure{\includegraphics[scale = .6]{figs/compFlowPics/airfoil_mesh.png}}
\subfigure{\includegraphics[scale=.3]{figs/SUPG.png}}
\end{figure}
\end{column}
\end{columns}
}

\section{The DPG Method}
\frame{
\frametitle{DPG: a minimum residual method via optimal testing}
Given a trial space $U$ and Hilbert test space $V$,
\[
b(u,v) = \ell(v) \Longleftrightarrow Bu = \ell, \quad 
\left.\begin{array}{cl}
\langle Bu,v\rangle_V &\coloneqq b(u,v)\\
\langle \ell,v\rangle_V &\coloneqq \ell(v).
\end{array}\right.
\]
We seek to minimize the \textcolor{red}{dual residual} over $U_h \subset U$
\[
J(u_h) = \frac{1}{2}\|Bu_h-\ell\|_{V'}^2 = \frac{1}{2}\left\|R_V^{-1}(Bu_h-\ell)\right\|_V^2.
\]
where $R_V: V \to V'$ is the isometric Riesz map
\[
\langle R_V v,\delta v\rangle_V \coloneqq(v, \delta v)_V, \quad \forall \delta v \in V.
\]
Conditions for minimization of the convex functional give
\[
b(u_h,v_{\delta u}) = \ell(v_{\delta u}), \quad \forall \delta u \in U_h, \quad v_{\delta u} \coloneqq R_V^{-1}B\delta u.
\]
}

@@

\setcounter{subfigure}{0}
\frame{
\frametitle{The graph test norm - near $L^2$ best approx for Stokes.}
\vspace{-.3cm}
\begin{figure}
\centering
\subfigure[Manufactured soln:\ $u_1$ error]{\includegraphics[scale=.235]{figs/stokes/u1_err.pdf}}
\subfigure[Manufactured soln:\ $p$ error]{\includegraphics[scale=.235]{figs/stokes/pressure_err.pdf}}
\subfigure[Cavity flow streamlines]{\includegraphics[scale=.245]{figs/stokes/streamlines.pdf}}
\subfigure[Second Moffat eddy]{\includegraphics[scale=.245]{figs/stokes/streamlines_zoom.pdf}}
\end{figure}
}

@@

\frame{
\frametitle{The graph test norm: problems under convection-diffusion}
The graph norm\footnote{\bibentry{Bui-ThanhDemkowiczGhattas11b}} for convection-diffusion gives exceptional stability.  %, this norm is defined elementwise
\begin{align*}
\|\left(v,\tau\right)\|_{V(K)}^2 =& \| \div \tau - \beta \cdot \grad v\|_{L^2(K)}^2 + 
\| \epsilon^{-1} \tau + \grad v \|_{L^2(K)}^2 +
\|v\|_{L^2(K)}^2.
\end{align*}
Problem with this test norm: approximability of test functions.
\begin{figure}[!h]
\centering
\includegraphics[scale=.16]{figs/opt.png}
\caption{Components of optimal test functions for flux $\widehat{f}_n$ on the \emph{right-hand} side of a unit element for $\epsilon = 0.01$. }
\label{fig:optTestBoundary}
\end{figure}
}

\frame{
\frametitle{Determining an alternative test norm}
%Recall the convection-diffusion bilinear form.  %Let $\boldsymbol U = \LRp{u,\sigma,\widehat{u},\widehat{f}_n}$. 
\vspace{-.85cm}
\begin{align*}%b\left(\left(u,\sigma, \widehat{u}, \widehat{f}_n\right),\left( v, \tau \right)\right) 
b(\boldsymbol U,\boldsymbol V) = \left(u,\div \tau - \beta \cdot \grad
v\right)_{\Oh} + \left(\sigma, \epsilon^{-1} \tau + \grad v\right)_{\Oh} + \text{boundary terms}
% - \LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gh} + \LRa{\widehat{f}_n,\jump{v} }_{\Gh}
\end{align*}
Recover $\nor{u}^2_{L^2(\Omega)}$ with conforming $\LRp{v,\tau}$ satisfying the \emph{adjoint equations}
\begin{align*}
\left.
\begin{array}{cl}
\div\tau - \beta \cdot \grad v   &= u\\
\frac{1}{\epsilon}\tau + \grad v &= 0
\end{array}
\right. ,
\quad
\text{boundary terms} = 0%\LRa{\jump{\tau\cdot n}, \widehat{u} }_{\Gamma}, \LRa{ \widehat{f}_n,\jump{v} }_{\Gamma} = 0
\end{align*}
``Necessary'' conditions for robustness --- 
\[
\nor{u}^2_{L^2(\Omega)} = b\LRp{{\boldsymbol U},\LRp{v,\tau}} = \frac{b\LRp{{\boldsymbol U},\LRp{v,\tau}}}{\nor{\LRp{v,\tau}}_V} \nor{\LRp{v,\tau}}_V \leq \nor{\boldsymbol U}_E \nor{\LRp{v,\tau}}_V
\]
Let $\lesssim$ denote a robust bound - \textcolor{red}{if $ \nor{\LRp{v,\tau}}_V \lesssim \|u\|_{L^2(\Omega)}$}, then we have that
\[
\nor{u}_{L^2(\Omega)} \lesssim \nor{\boldsymbol U}_E
\]
\textbf{Main idea: the \textcolor{red}{test norm} should measure \textcolor{red}{adjoint solutions} robustly.}
}

@@

\begin{figure}[!h]
\centering
\subfigure[Dirichlet inflow $u=u_0$]{\includegraphics[scale=.35]{figs/dirichletBC.png}}
\subfigure[``Convection'' inflow $u-\epsilon u' \approx u_0$]{\includegraphics[scale=.35]{figs/newBC.png}}
\caption{DPG solutions to convection-diffusion for both inflow conditions using an $H^1$ test norm.}
\end{figure}
}

@@

%On domain $\Omega = [0,1]^2$, with $\beta = (1,0)^T$, $ f = 0$ and boundary conditions
%\begin{align*}
%\widehat{\beta_nu - \sigma_n} &= \widehat{f}_n = u_0, \quad \beta_n \leq 0\\
%\widehat{u} &= 0, \quad \beta_n > 0
%\end{align*}
Adaptive refinement using Camellia\footnote{\bibentry{Camellia}} for a boundary layer solution.
%\begin{figure}
%\centering
%\subfigure{
%\includegraphics[scale=.23]{figs/wallBC_exact_u.png}
%}
%\subfigure{
%\includegraphics[scale=.23]{figs/wallBC_exact_sigx.png}
%}
%\subfigure{
%\includegraphics[scale=.23]{figs/wallBC_exact_sigy.png}
%}
%\caption{Exact solution for $u$, $\sigma_x$, and $\sigma_y$ for $\epsilon = .01$, $C_1 = 1$, $C_n=0$, $n\neq 1$}
%\end{figure}
\begin{figure}
\centering
\subfigure{
\includegraphics[scale=.33]{figs/errorrates_wallBC.png}
}
\subfigure{
\includegraphics[scale=.33]{figs/L2energyratio_wallBC.png}
}
%\subfigure{
%\includegraphics[scale=.22]{figs/u_pointdiff_wallBC.png}
%}
\caption{$L^2$/energy errors and their ratio for $\epsilon = .01, .001, .0001$.}
\end{figure}
}

@@

\frame{
\frametitle{Extrapolation of test norms}
%\begin{columns}
%\begin{column}{.48\textwidth}
Convection-diffusion:
\begin{align*}
\div \left(\textcolor{red}{\beta u} - \textcolor{blue}{\sigma}\right) &= f\\
\frac{1}{\epsilon}\sigma - {\grad u} &= 0.
\end{align*}
Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},w\}$,
\begin{align*}
\div \left(\textcolor{red}{A_{\rm invisc}U} - \textcolor{blue}{A_{\rm visc}\Sigma}\right) &= R_{\rm conserv}(U,\Sigma)\\
E_{\rm visc} \Sigma - \grad U &= R_{\rm constit}(U,\Sigma)
\end{align*}
where $R_{\rm conserv}(U,\Sigma)$ and $R_{\rm constit}(U,\Sigma)$ are the conservation/constitutive residuals.
}
%\addtocounter{framenumber}{-1}
\addtocounter{framenumber}{-1}
\frame{
\frametitle{Extrapolation of test norms}
%\begin{columns}
%\begin{column}{.48\textwidth}
Convection-diffusion:
\begin{align*}
\div \left(\beta u - \sigma\right) &= f\\
\textcolor{red}{\frac{1}{\epsilon}\sigma} - \textcolor{blue}{\grad u} &= 0.
\end{align*}
Navier-Stokes: defining vector variables $U = \{\rho,u_1,u_2,T\}$ and $\Sigma = \{{\boldsymbol \sigma},\mathbf{q},w\}$,
\begin{align*}
\div \left({A_{\rm invisc}U} - {A_{\rm visc}\Sigma}\right) &= R_{\rm conserv}(U,\Sigma)\\
\textcolor{red}{E_{\rm visc} \Sigma} - \textcolor{blue}{\grad U} &= R_{\rm constit}(U,\Sigma)
\end{align*}
where $R_{\rm conserv}(U,\Sigma)$ and $R_{\rm constit}(U,\Sigma)$ are the conservation/constitutive residuals.
}

@@

\frame{
\frametitle{Refinement level 0}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u0.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T0.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh0.png}}
\end{figure}
}
\addtocounter{framenumber}{-1}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 1}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u1.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T1.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh1.png}}
\end{figure}
}
\addtocounter{framenumber}{-1}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 2}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u2.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T2.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh2.png}}
\end{figure}
}
\addtocounter{framenumber}{-1}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 3}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u3.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T3.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh3.png}}
\end{figure}
}
\addtocounter{framenumber}{-1}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 4}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u4.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T4.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh4.png}}
\end{figure}
}
\addtocounter{framenumber}{-1}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 5}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u5.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T5.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh5.png}}
\end{figure}
}
\addtocounter{framenumber}{-1}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 6}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u6.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T6.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh6.png}}
\end{figure}
}
\addtocounter{framenumber}{-1}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 7}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u7.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T7.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh7.png}}
\end{figure}
}
\addtocounter{framenumber}{-1}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 8}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u8.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T8.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh8.png}}
\end{figure}
}
\addtocounter{framenumber}{-1}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 9}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u9.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T9.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh9.png}}
\end{figure}
}
\addtocounter{framenumber}{-1}
\setcounter{subfigure}{0}

\frame{
\frametitle{Refinement level 10}
\begin{figure}
\centering
\subfigure[$u_1$]{\includegraphics[scale = .23]{figs/propMovie/u10.png}}
\subfigure[$T$]{\includegraphics[scale = .23]{figs/propMovie/T10.png}}
\subfigure{\includegraphics[scale = .35]{figs/propMovie/Mesh10.png}}
\end{figure}
}
\addtocounter{framenumber}{-1}
\setcounter{subfigure}{0}

@@

%\input{futureWork}
\input{extendedSlides}
